### 2020-08-12 thesis/chap_1.tex
updates captions chap 1

% PCA
\begin{figure}[h!]
  \centering
    \includegraphics[width=0.9\textwidth]{thesis/figures/PCA_data_profiles.png}
  \caption{Ordination of land use data (proportions) for municipalities. Groups are derived from clustering in \ref{fig:clustervals}}
  \label{fig:PCAvals}
\end{figure}

% MAP
\begin{figure}[h!]
  \centering
    \includegraphics[width=\textwidth]{thesis/figures/profiles_land_use.png}
  \caption{Geographical distribution of the 5 profiles identified in \ref{fig:clustervals} and \ref{fig:PCAvals}.}
  \label{fig:mapvals}
\end{figure}

@@

% PCA
\begin{figure}[h!]
  \centering
    \includegraphics[width=0.9\textwidth]{thesis/figures/PCA_trans_profiles.png}
  \caption{Ordination of land use transition data for municipalities. Groups are derived from clustering \ref{fig:clustertrans}}
  \label{fig:PCAtrans}
\end{figure}

%MAP
\begin{figure}[h!]
  \centering
    \includegraphics[width=\textwidth]{thesis/figures/transition_prof_map.png}
  \caption{Geographical distribution of the 4 change profiles identified in \ref{fig:clustertrans} and \ref{fig:PCAtrans}.}
  \label{fig:maptrans}
\end{figure}

@@

\begin{table}[h!]
\centering
\caption{Variable importance (gini impurity index) for both models - non-categorical variables only}
\label{tab:varimp}
\begin{tabular}{lcc}
\hline
\hline
\multicolumn{1}{c}{\multirow{2}{*}{Variable}} & \multicolumn{2}{c}{Model} \\ \cline{2-3} 
\multicolumn{1}{c}{} & \multicolumn{1}{l}{Urbanisation} & \multicolumn{1}{l}{Agricultural expansion} \\ \hline
Distance from urban land & 756.8292 & 1787.357 \\
Size of forest patch & 548.5826 & 5373.270 \\
Elevation & 580.9726 & 1823.918 \\
Population change & 447.1120 & 1138.319 \\
Income & 390.5668 & 1108.612 \\ 
\hline
\end{tabular}
\end{table}

@@

\begin{table}[!htbp] \centering 
  \caption{$R^{2}$, AUC, and average precision values for both models and both validation sets.} 
  \label{tab:R_squares_AUC} 
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Model & Validation set & $R^{2}$ & AUC & Average Precision \\ 
\hline \\[-1.8ex] 
Agricultural Expansion & Spatial & $0.566$ & $0.931$ & $0.652$ \\ 
Agricultural Expansion &  Temporal & $0.566$ & $0.841$ & $0.023$ \\ 
Urbanization & Spatial & $0.573$ & $0.939$ & $0.234$ \\ 
Urbanization & Temporal & $0.573$ & $0.921$ & $0.250$ \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

@@

\begin{table}[!htbp] \centering 
\caption{AUC values for both models in resampled 10 folds CCV.} 
\label{tab:R_squares_resample} 
\begin{tabular}{@{\extracolsep{5pt}} cccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Model & Mean AUC +/- Std \\ 
\hline \\[-1.8ex] 
Agricultural Expansion & $0.929 \pm 0.002$ \\ 
Urbanisation & $0.938 \pm 0.002$ \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

@@

\begin{table}[!htbp] \centering
\caption{AUC and average precision values for the predictions of the land use change model.} 
\label{tab:historic_metrics} 
\begin{tabular}{lcccc}
\hline
\hline
\multicolumn{1}{c}{Model} & \begin{tabular}[c]{@{}c@{}}Mean AUC\\ (Averaged \\ Surface)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Mean Precision\\ (Averaged \\ Surface)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Mean AUC +/- Std\\ (All iterations \\ averaged)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Mean Precision +/- Std\\ (All Iterations \\ averaged)\end{tabular} \\ \hline
\begin{tabular}[c]{@{}l@{}}Agricultural \\ Expansion\end{tabular} & $0.858$ & $0.383$ & $0.669 \pm 0.001$ & $0.105 \pm 0.001$ \\
Urbanisation & $0.784$ & $0.287$ & $0.618 \pm 0.001$ & $0.102 \pm 0.001$ \\ \hline
\end{tabular}
\end{table}

@@

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=\textwidth]{thesis/figures/historic_compare_urb.png}
}
 \caption{Comparison between mean probability of urbanization and actual urbanization observed between 1990 and 2010.}
 \label{fig:compare_urb}
\end{figure}

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=\textwidth]{thesis/figures/historic_compare_agex.png}
}
 \caption{Comparison between mean probability of agricultural expansion and actual agricultural expansion observed between 1990 and 2010.}
 \label{fig:compare_agex}
\end{figure}

@@

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=\textwidth]{thesis/figures/bar_both.png}
}
 \caption{Comparison land use class frequencies in 2010, and 2100 for both the BAU and Reforestation scenarios.}
 \label{fig:bar_both}
\end{figure}

@@

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=\textwidth]{thesis/figures/original_hists.png}
}
 \caption{Histograms of flow values for the year 2010 comparing the historic model run with observations.}
 \label{fig:hist_historic}
\end{figure}

@@

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=\textwidth]{thesis/figures/connectivity_decrease_x5species_historic.png}
}
 \caption{Change in mean flow (in \% of the the 1990 flow) between 1990 and 2010, contrasting observed change and simulated chnage.}
 \label{fig:flow_historic}
\end{figure}

@@

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=\textwidth]{thesis/figures/connectivity_decrease_x5species_chap1.png}
}
 \caption{Change in mean flow (in \% of the the 2010 flow) between 2010 and 2100, contrasting BAU scenario (solid line) with other land use change scenarios.}
 \label{fig:flow_linear_1}
\end{figure}

@@

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=\textwidth]{thesis/figures/radar_ggradar_chap1.png}
}
 \caption{Change in mean flow (in \% of the the 2010 flow) between 2010 and 2100, contrasting BAU scenario (solid line) with other land use change scenarios.}
 \label{fig:flow_radar_1}
\end{figure}

@@

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=\textwidth]{thesis/figures/hist_chap1.png}
}
 \caption{Histograms of flow values change.}
 \label{fig:hist_1}
\end{figure}

@@

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=\textwidth]{thesis/figures/surf_chap1.png}
}
 \caption{Change in identified features (partly pinch-points).}
 \label{fig:surf_linear_1}
\end{figure}

@@

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=\textwidth]{thesis/figures/surf_radar_chap1.png}
}
 \caption{Change in identified features (partly pinch-points.}
 \label{fig:surf_radar_1}
\end{figure}

>>>>

% PCA
\begin{figure}[h!]
  \centering
    \includegraphics[width=0.9\textwidth]{thesis/figures/PCA_data_profiles.png}
  \caption{Ordination of land use data (proportions) for municipalities. Groups are derived from clustering in figure \ref{fig:clustervals}.}
  \label{fig:PCAvals}

% MAP
  \centering
    \includegraphics[width=\textwidth]{thesis/figures/profiles_land_use.png}
  \caption{Geographical distribution of the 5 profiles identified in figures \ref{fig:clustervals} and \ref{fig:PCAvals}.}
  \label{fig:mapvals}
\end{figure}

@@

% PCA
\begin{figure}[h!]
  \centering
    \includegraphics[width=0.9\textwidth]{thesis/figures/PCA_trans_profiles.png}
  \caption{Ordination of land use transition data for municipalities. Groups are derived from clustering in figure \ref{fig:clustertrans}.}
  \label{fig:PCAtrans}

%MAP
  \centering
    \includegraphics[width=\textwidth]{thesis/figures/transition_prof_map.png}
  \caption{Geographical distribution of the 4 change profiles identified in figures \ref{fig:clustertrans} and \ref{fig:PCAtrans}.}
  \label{fig:maptrans}
\end{figure}

@@

\begin{table}[h!]
\centering
\caption{Variable importance (gini impurity index) for both random forest models - non-categorical variables only.}
\label{tab:varimp}
\begin{tabular}{lcc}
\hline
\hline
\multicolumn{1}{c}{\multirow{2}{*}{Variable}} & \multicolumn{2}{c}{Model} \\ \cline{2-3} 
\multicolumn{1}{c}{} & \multicolumn{1}{l}{Urbanisation} & \multicolumn{1}{l}{Agricultural expansion} \\ \hline
Distance from urban land & 756.8292 & 1787.357 \\
Size of forest patch & 548.5826 & 5373.270 \\
Elevation & 580.9726 & 1823.918 \\
Population change & 447.1120 & 1138.319 \\
Income & 390.5668 & 1108.612 \\ 
\hline
\end{tabular}
%\end{table}

@@

%\begin{table}[!htbp] \centering 
  \caption[$R^{2}$, AUC, and average precision values for both models and both validation sets.]{$R^{2}$, AUC, and average precision values for both models and both validation sets - The spatial validation set corresponds to the testing partition for the 1990-2000 timestep, whereas the temporal validation set corresponds to the entire data of the 2000-2010 timestep.} 
  \label{tab:R_squares_AUC} 
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Model & Validation set & $R^{2}$ & AUC & Average Precision \\ 
\hline \\[-1.8ex] 
Agricultural Expansion & Spatial & $0.566$ & $0.931$ & $0.652$ \\ 
Agricultural Expansion &  Temporal & $0.566$ & $0.841$ & $0.023$ \\ 
Urbanization & Spatial & $0.573$ & $0.939$ & $0.234$ \\ 
Urbanization & Temporal & $0.573$ & $0.921$ & $0.250$ \\ 
\hline \\[-1.8ex] 
\end{tabular} 
%\end{table}

@@

%\begin{table}[!htbp] \centering 
\caption{AUC values for both models in resampled 10 folds CCV.} 
\label{tab:R_squares_resample} 
\begin{tabular}{@{\extracolsep{5pt}} cccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Model & Mean AUC +/- Std \\ 
\hline \\[-1.8ex] 
Agricultural Expansion & $0.929 \pm 0.002$ \\ 
Urbanisation & $0.938 \pm 0.002$ \\ 
\hline \\[-1.8ex] 
\end{tabular}
%\end{table}

@@

%\begin{table}[!htbp] \centering
\caption{AUC and average precision values for the predictions of the land use change model.} 
\label{tab:historic_metrics} 
\begin{tabular}{lcccc}
\hline
\hline
\multicolumn{1}{c}{Model} & \begin{tabular}[c]{@{}c@{}}Mean AUC\\ (Averaged \\ Surface)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Mean Precision\\ (Averaged \\ Surface)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Mean AUC +/- Std\\ (All iterations \\ averaged)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Mean Precision +/- Std\\ (All Iterations \\ averaged)\end{tabular} \\ \hline
\begin{tabular}[c]{@{}l@{}}Agricultural \\ Expansion\end{tabular} & $0.858$ & $0.383$ & $0.669 \pm 0.001$ & $0.105 \pm 0.001$ \\
Urbanisation & $0.784$ & $0.287$ & $0.618 \pm 0.001$ & $0.102 \pm 0.001$ \\ \hline
\end{tabular}
\end{table}

@@

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/historic_compare_urb.png}
}
 \caption[Predicted probability of urbanization vs observed urbanization between 1990 and 2010.]{Predicted probability of urbanization (left) vs observed urbanization (right) between 1990 and 2010.}
 \label{fig:compare_urb}
%\end{figure}

%\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/historic_compare_agex.png}
}
 \caption[Predicted probability of agricultural expansion vs observed agricultural expansion between 1990 and 2010.]{Predicted probability of agricultural expansion (left) vs observed agricultural expansion (right) between 1990 and 2010.}
 \label{fig:compare_agex}
\end{figure}

@@

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/bar_both.png}
}
 \caption{Land use class frequencies in 2010 (observed) and 2100 (predicted) for the BAU and Reforestation scenarios (under baseline climate scenario).}
 \label{fig:bar_both}
\end{figure}

@@

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/original_hists.png}
}
 \caption{Histograms of flow values for the year 2010 comparing the historic model run (1990-2010) with observations.}
 \label{fig:hist_historic}
\end{figure}

@@

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/connectivity_decrease_x5species_historic.png}
}
 \caption{Change in mean flow (in \% of the the 1990 flow) between 1990 and 2010, contrasting observed historic change (1990-2010) and simulated change from historic model run.}
 \label{fig:flow_historic}
\end{figure}

@@

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/connectivity_decrease_x5species_chap1.png}
}
 \caption{Change in mean flow (in \% of the the 2010 flow) between 2010 (observed) and 2100 (predicted), contrasting BAU scenario (solid line) with other land use change scenarios - linear graph.}
 \label{fig:flow_linear_1}
\end{figure}

@@

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/radar_ggradar_chap1.png}
}
 \caption{Change in mean flow (in \% of the the 2010 flow) between 2010 (observed) and 2100 (predicted), contrasting BAU scenario with other land use change scenarios - radar graph.}
 \label{fig:flow_radar_1}
\end{figure}

@@

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/hist_chap1.png}
}
 \caption{Histograms of flow values for all species and scenarios, for 2010 (observed) and 2100 (predicted).}
 \label{fig:hist_1}
\end{figure}

@@

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/surf_chap1.png}
}
 \caption{Change in the number of features (in \% of the the 2010 flow) identified by the SURF analyssis between 2010 (observed) and 2100 (predicted), contrasting BAU scenario with other land use change scenarios - linear graph.}
 \label{fig:surf_linear_1}
\end{figure}

@@

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/surf_radar_chap1.png}
}
 \caption{Change in the number of features (in \% of the the 2010 flow) identified by the SURF analyssis between 2010 (observed) and 2100 (predicted), contrasting BAU scenario with other land use change scenarios - radar graph.}
 \label{fig:surf_radar_1}
\end{figure}
